Responses to the Reviewers' Comments

### 2024-10-21 Response/Paper_Res.tex
Rev_V6.5

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to vanila DQN and DDQN methods, while providing a substantial improvement of at least 34.8\% in average QoE. This advantage is achieved through prioritizing MD's QoE preferences, resulting in improvements of at least 12.2\%, 11.7\%, and 10.8\% in the average number of completed tasks, task delay, and energy consumption, respectively, when compared to the distributed and collective DRL-based offloading algorithm (DCDRL) \cite{qiu2020distributed} and several benchmark methods.}

@@

\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
					\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
					\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a single MEC system model  \\\midrule
					\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a single MEC system model \\\midrule				
					\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
					\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
					\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
					\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
					\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
					\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
					\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
					\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
					\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
					\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
					\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
					\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
					\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
					\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
					QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
					\toprule
			\end{tabular}}
			\label{table1}}
	\end{table*}

@@

	\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a single MEC system model  \\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a single MEC system model \\\midrule				
				\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{wu2023multi} 1& Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
		\end{tabular}}
		\label{table111}}
\end{table*}

We have also revised Secion I accordingly to make it consistent with the updated contents of related work. The following paragraph shows the changes we have made in Section I of the revised manuscript.

%\textcolor{blue}{\,\,\,\,To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
%	While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
%	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.} \vspace{2mm}

\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}

 }
\end{my}

@@

\underline{Authors' Reply}: The proposed approach is designed to balance and prioritize QoE factors based on individual mobile device requirements while considering the dynamic workloads of edge nodes (EN). The QECO algorithm captures the dynamics of the MEC environment by integrating the Dueling Double Deep Q-Network (D3QN) model with Long Short-Term Memory (LSTM) networks. These algorithms address the QoE maximization problem by efficiently utilizing resources from both mobile devices and edge servers.

@@

	\item D3QN: By integrating both Double Q-learning and Dueling Network Architectures, D3QN overcomes overestimation bias in action-value predictions and accurately identifies the relative importance of states and actions. This significantly improves the model's ability to make accurate predictions, providing a foundation for enhanced offloading strategies.\vspace{2mm}

	\item LSTM: The incorporation of LSTM networks allows the model to continuously estimate dynamic workloads at edge servers. This feature is crucial for dealing with limited global information and adapting to an uncertain environment. By predicting the future workload of edge servers, mobile devices can effectively adjust their offloading strategies to achieve higher QoE.\vspace{2mm}

@@

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to vanila DQN and DDQN methods, while providing a substantial improvement of at least 34.8\% in average QoE. This advantage is achieved through prioritizing MD's QoE preferences, resulting in improvements of at least 12.2\%, 11.7\%, and 10.8\% in the average number of completed tasks, task delay, and energy consumption, respectively, when compared to the distributed and collective DRL-based offloading algorithm (DCDRL) \cite{qiu2020distributed} and several benchmark methods.}

@@

(b) We have considered the selected edge server and indecated offloaded task in previous version of manuscript, in Equations (16) and (17)

We need to explain whether it was correct before. Why we didn't have y before? You can say that we had considered the selected edge server before, but to make it more clear, we have included y to show the edge server selection.

To address the reviewer’s comment regarding the inclusion of the indicator function $y_{i,j}(t)$, we have revised Equations (16) and (17) in Section III, and Equations (21) and (22) in Section IV of the revised manuscript, as follows:
\setcounter{equation}{16}
		\begin{my}{1cm}{1cm}
	\rev{
		{\ \color{black}
%\begin{alignat}{1}
%	E_{i,j}^{\text{I}}(t) = \textcolor{blue}{\sum_{\mathcal{J}} y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
%	\label{16}
%\end{alignat}
\begin{alignat}{1}
	E_i^{\text{O}}(t) = E_i^{\text{T}}(t) + \sum_{\mathcal{J}} \textcolor{blue}{y_{i,j}(t)} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t).
	\label{17}
\end{alignat}
\setcounter{equation}{20}
	\hspace{-10mm}$\mathcal{D}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) =$
\begin{alignat}{1}
 \hspace{-10mm}(1-x_i(t))\Big(l_i^{\text{C}}(t) - t + 1\Big)  +  x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t'=t}^{T} \mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)} \, l_{i,j}^{\text{E}}(t') - t +1\bigg),
	\label{21}  
\end{alignat} 
\begin{alignat}{1}
	\hspace{-10mm}\mathcal{E}_i(\boldsymbol{s}_i(t),\boldsymbol{a}_i(t)) = (1-x_i(t)) E_i^{\text{L}}(t)+  x_i(t)\bigg( \sum\limits_{\mathcal{J}} \sum\limits_{t^{'}=t}^{T}\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big) \textcolor{blue}{y_{i,j}(t)}  E_i^{\text{O}}(t)  \bigg).
	\label{22}  
\end{alignat}
}}
\end{my}

@@

@@

\underline{Authors' Reply}: (a) We have carefully repaced the phrase "battery level" with "energy state" throughout the revised manuscript. \newline

>>>>

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to vanilla DQN and DDQN methods, while providing a substantial improvement of at least 34.8\% in average QoE. This advantage is achieved through prioritizing MD's QoE preferences, resulting in improvements of at least 12.2\%, 11.7\%, and 10.8\% in the average number of completed tasks, task delay, and energy consumption, respectively, when compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed}, the distributed and collective DRL-based offloading algorithm (DCDRL) \cite{qiu2020distributed}, and several benchmark methods.}

@@

\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
					\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
 					\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
				\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
				\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a single MEC system model \\\midrule				
				%\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
				\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
				\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
				\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a single MEC system model  \\\midrule
				\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
				\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
				\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
				\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
				\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
				\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
				\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
				\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
				QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
				\toprule
				\end{tabular}}
				\label{table1}}
\end{table*}

@@

	\begin{table*}[htbp]\textcolor{blue}{
		\renewcommand{\arraystretch}{0.6}
		\captionsetup{name=TABLE}
		\caption{\textcolor{blue}{Comparison of Related Works \vspace{4mm}}}
		\scalebox{0.7}{%
			\begin{tabular}{ lp{3.4cm}p{4.5cm}p{5.2cm}p{1.7cm}p{3.1cm}p{4.6cm}l} 
				\toprule
				\textbf{Paper} & \textbf{Scenario} &  \textbf{Problem} &  \textbf{Objective} &  \textbf{Model} & \textbf{Method} &  \textbf{Drawbacks}  \\ \midrule
 					\cite{liu2021learn} & MEC & Resource allocation and computation offloading & Minimize execution cost & POMDP & Multi-agent actor-critic network &  Not consider delay-sensitive tasks \\\midrule
\cite{wu2023computation}  & SDN-based MEC & Stochastic game-based resource allocation & Minimize energy consumption and processing delay & MDP & Multi-agent RL & Not consider tasks with maximum delay tolerance\\\midrule
\cite{zhou2021deep} & heterogeneous MEC & Resource allocation and computation offloading & Minimize energy consumption of the entire system & MDP & DDQN & Only for a single MEC system model \\\midrule				
%\cite{huang2019deep} & Wireless-powered MEC & Computation offloading and resource allocations & Maximize computation rate & MIP & DQN & Not consider delay-sensitive tasks \\\midrule
\cite{wu2024privacy} & MEC-based IIoT  & Joint power allocation and computation offloading  & Optimization of privacy protection and quality of service. & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
\cite{dai2020edge} & MEC & Resource allocation and computation offloading & Minimize energy consumption & MDP & DDPG & Not take user's demand into consideration \\\midrule
\cite{zhao2019deep} & MEC & User association and resource allocation & Optimize downlink utility & MDP & Multi-agent D3QN & Not consider system delay and energy consumtion \\\midrule
\cite{liao2023online} & Queuing-based MEC & Online computation offloading & Minimize computation delay and energy consumption & MDP & DDQN & Only for a single MEC system model  \\\midrule
\cite{wu2024combining}  & Queuing-based IIoT MEC & Privacy aware computation offloading & Optimization of computation rate and energy consumption & MDP & Actor-critic network  & Not take user's demand into consideration \\\midrule
\cite{Bolourian-WCL24}  & Queuing-based MEC with EHs& Energy harvesting  computation offloading & Minimize drop rate and energy consumption. & MDP  & DQN & Not consider computation delay  \\\midrule
\cite{huang2021deadline} & Queuing-based MEC & Computation offloading & Optimize drop rate and energy consumption & POMDP & DDPG & Not consider computation delay \\ \midrule
\cite{gong2022edge} & MEC-based IIoT & Resource allocation and computation offloading & Minimize task computation delay and energy consumption & MDP & DRL & Not take user's demand into consideration\\\midrule
\cite{sun2024hierarchical} & MEC & Computation offloading and service caching & Minimize average service delay & MDP & hierarchical DRL & Not consider system energy consumtion \\\midrule
\cite{wu2023multi} & Queuing-based IIoT MEC & Computation offloading & Optimize delay and energy consumption & POMDP & Multi-agent PPO&  Not consider tasks with maximum delay tolerance \\\midrule
\cite{9253665} &  Queuing-based MEC &  Computation offloading & Minimize drop rate and computation delay. & MDP & D3QN + LSTM & Not consider system energy consumtion\\\midrule
\cite{gao2022large} & Queuing-based heterogeneous MEC & Decentralized computation offloading & Optimize system cost and completion rates & MDP & Multi-agent actor-critic network& Not take user's demand into consideration \\\midrule
QECO &  Queuing-based MEC &  Computation offloading & Maximize the QoE of each MD individually &MDP & D3QN + LSTM & \\
\toprule
\end{tabular}}
\label{table1}}
\end{table*}

%\vspace{6mm}
%
%We have also revised Secion I accordingly to make it consistent with the updated contents of related work. The following paragraph shows the changes we have made in Section I of the revised manuscript.
%
%
%\vspace{6mm}

%
%\begin{my}{1cm}{1cm}
%	\rev{ 
%	
%	\dots
%
%%\textcolor{blue}{\,\,\,\,To cope with the dynamic nature of the network, recent research has proposed several task offloading algorithms using machine learning methods. In particular, reinforcement learning (RL) \cite{mnih2015human} holds promises to determine optimal decision-making policies by capturing the dynamics of environments and learning strategies for accomplishing long-term objectives.
%%	While RL-based methods have demonstrated their effectiveness in handling network dynamics, task offloading still encounters several challenges that require further attention. 
%%	QoE is a time-varying performance measure that reflects user satisfaction and is not affected only by delay \cite{guo2022energy}, but also by energy consumption \cite{tang2022uav}. Albeit some existing works have investigated the trade-off between delay and energy consumption \cite{li2022joint}, they fail to properly address the user demands and fulfill QoE requirements. A more comprehensive approach is required to address the dynamic requirements of individual users in real-time scenarios with multiple MDs and ENs.} \vspace{2mm}
%
%
%
%
%\textcolor{blue}{\,\,\,\,In this study, we delve into the computation task offloading problem in MEC systems, where strict task processing deadlines and energy constraints can adversely affect the system's performance. To mitigate these challenges, we propose a distributed QoE-oriented computation offloading (QECO) algorithm, leveraging DRL to enhance decision-making in real-time and uncertain environments. Unlike conventional approaches that require global information, QECO allows MDs to make offloading decisions and select the most suitable EN based on locally available data, including task size, queue status, energy levels, and the historical workload of ENs. Specifically, QECO integrates predictive models to continuously estimate dynamic workloads at ENs, enabling MDs to proactively adjust their offloading strategies in real time, even under high network volatility. With a focus on task completion, delay, and energy consumption, QECO quantifies the QoE for MDs and strikes an optimal balance among these factors. By adopting the appropriate policy based on each MD’s specific requirements at any given time, the QECO algorithm significantly improves the QoE for individual users.}
%
%\dots
%
% }
%\end{my}

@@

\underline{Authors' Reply}: The proposed approach is designed to balance and prioritize QoE factors based on individual mobile device requirements while considering the dynamic workloads at the edge servers. The QECO algorithm captures the dynamics of the MEC environment by integrating the Dueling Double Deep Q-Network (D3QN) model with Long Short-Term Memory (LSTM) networks. These algorithms address the QoE maximization problem by efficiently utilizing resources from both mobile devices and edge servers.

@@

	\item D3QN: By integrating both Double Q-learning and Dueling Network Architectures, D3QN overcomes overestimation bias in action-value predictions and accurately identifies the relative importance of states and actions. This improves the model's ability to make accurate predictions, providing a foundation for enhanced offloading strategies.\vspace{2mm}

	\item LSTM: Incorporating LSTM networks allows the model to continuously estimate dynamic workloads at edge servers. This feature is crucial for dealing with limited global information and adapting to an uncertain environment. By predicting the future workload of edge servers, mobile devices can effectively adjust their offloading strategies to achieve higher QoE.\vspace{2mm}

@@

	\item \textit{Performance Evaluation:} \textcolor{blue}{We conduct comprehensive experiments to evaluate the QECO's performance under various computational workloads, as well as its training convergence with different techniques and hyperparameters. The results demonstrate that our algorithm effectively utilizes the computing resources of MDs and ENs, addressing the dynamic workloads at ENs. It converges more quickly compared to vanilla DQN and DDQN methods while providing a substantial improvement by 37.4\%\,--\,29.8\% in average QoE compared to the potential game-based offloading algorithm (PGOA)~\cite{yang2018distributed} and the distributed and collective DRL-based offloading algorithm (DCDRL)~\cite{qiu2020distributed}, respectively.}

@@

(b) Please note that for any queue in the system model, we assume that once a task is completed within a time slot, the next task in the queue will begin processing at the start of the next time slot. Besides, we assume that during each time slot, a mobile device either receives a new task or does not, considering the small duration of each time slot ($\tau = 0.1$ seconds). Based on these assumptions, in the previous version of the manuscript, we utilized the indicator function $\mathbbm{1}\big(z_{i,j}^{\text{E}}(t') = z_i(t)\big)$ in Equations (21) and (22) to indicate edge server selection.
However, to address the reviewer’s comment and make the edge server selection more clear, we have included $y_{i,j}(t)$ into Equations (16) and (17) in Section III of the revised manuscript, as follows:

\setcounter{equation}{15}
		\begin{my}{1cm}{1cm}
	\rev{
		{\ 
\begin{alignat}{1}
	E_{i}^{\text{I}}(t) =  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t)} D_{i,j}^{\text{E}}(t) p_i^{\text{I}} \tau, %= {\lambda_{i,j}^{\text{E}}(t) \rho_i(t) \over \mathcal{B}_j(t) f_j^{\text{E}}} p_i^{\text{I}},
	\label{16}
\end{alignat}
\begin{alignat}{1}
	\textcolor{blue}{E_i^{\text{O}}(t) = E_i^{\text{T}}(t) +  \textcolor{blue}{\sum_{\mathcal{J}}y_{i,j}(t) \,} E_{i,j}^{\text{E}}(t) + E_i^{\text{I}}(t)}.
	\label{17}
\end{alignat}
}}
\end{my}

@@

	\item \textbf{PGOA}~\cite{yang2018distributed}: \dots\vspace{1mm}

	\color{blue}
	\item \textcolor{blue}{\textbf{DCDRL}~\cite{qiu2020distributed}: This method is based on the actor-critic framework \cite{NIPS1999_6449f44a}, which underpins many state-of-the-art DRL algorithms, such as DDPG \cite{lillicrap2015continuous}, and PPO \cite{schulman2017proximal}. This method is designed for distributed computation offloading in a queuing-based MEC environment.}

@@

\underline{Authors' Reply}: (a) We have carefully repaced the phrase "battery level" with "energy level" throughout the revised manuscript. \newline
